\documentclass[10pt,a4paper,sans]{article}

% --- PACKAGES ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.6in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{multicol}

% --- STYLING ---
\definecolor{linkblue}{RGB}{0, 0, 238}
\hypersetup{colorlinks=true, linkcolor=linkblue, urlcolor=linkblue}
\urlstyle{same}

\titleformat{\section}{\large\bfseries\uppercase}{}{0pt}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{6pt}
\setlist[itemize]{leftmargin=1.5em, noitemsep, topsep=2pt}

\begin{document}

% --- HEADER ---
    \begin{center}
        {\huge \textbf{DANIEL MROCZKA}} \\
        \vspace{2pt}
        \textbf{Senior Java Developer | Passion Driven Developer} \\
        \vspace{4pt}
        1220 Vienna, Austria | \href{mailto:daniel.mroczka@gmail.com}{daniel.mroczka@gmail.com} \\
        \href{https://www.linkedin.com/in/danielmroczka}{linkedin.com/in/danielmroczka}
    \end{center}

% --- SUMMARY ---


    \section{Summary}
    Self-motivated, self-reliant, and quick learner Passion Driven Developer with a background in Java SE, Java EE, and Databases. Over 25 years of experience in aviation/travel, petrol, automation, consulting, finance, and banking. 18 years of experience in international teams and projects. Always interested in learning new technologies and walking on unbeaten paths while creating high-quality, usable software.

% --- WORK EXPERIENCE ---


    \section{Work Experience}

    \noindent \textbf{Erste Digital GmbH (Vienna)} \hfill \textbf{IV.2023 -- Present} \\
    \textit{Senior Java Developer}
    \begin{itemize}
        \item Development and maintenance of the Transaction module and Country Adaptor.
        \item Supporting banking operations across seven countries in the CEE region.
    \end{itemize}

    \vspace{6pt}
    \noindent \textbf{Dynatrace Austria GmbH (Vienna)} \hfill \textbf{III.2021 -- III.2023} \\
    \textit{Senior Java Developer}
    \begin{itemize}
        \item Implementation of Grail (3rd gen storage for logs and metrics).
        \item Scaled and distributed data ingestion; member of the Engineering Productivity Guild.
        \item Introduced self-monitoring, dashboards, and inter-team collaboration tools.
    \end{itemize}

    \vspace{6pt}
    \noindent \textbf{iov42 British-Austrian Startup (Vienna)} \hfill \textbf{VIII.2019 -- XI.2021} \\
    \textit{Senior Java Developer}
    \begin{itemize}
        \item Implemented prototypes and microservices based on core Blockchain platform.
        \item Developed Carbon Credit Ecosystem (CCE) and KYC use cases for Banking and Telecom.
    \end{itemize}

    \vspace{6pt}
    \noindent \textbf{Automic GmbH (Broadcom Inc.)} \hfill \textbf{XI.2018 -- IV.2019} \\
    \textit{Senior Java Engineer}
    \begin{itemize}
        \item Implemented features in Rule Engine for the Intelligence Automation team.
        \item Maintenance of the Automation Web Interface (AWI) project.
    \end{itemize}

    \vspace{4pt}
    \noindent \textit{Earlier experience: EBCONT (2014-2018), Roxcel Group (2012-2014), OpenJaw Technologies (2011-2012), Anachron (2010-2011), Sabre Holdings (2006-2010), Fortis Bank (2005-2006).}

% --- TECHNICAL SKILLS ---


    \section{Technical Skills}
    \begin{itemize}
        \item \textbf{Languages:} Java, Groovy, Kotlin, SQL, PL/SQL, JavaScript.
        \item \textbf{Frameworks:} Spring (Boot, Cloud, Data, MVC), Hibernate, JPA, JAX-RS, Vaadin.
        \item \textbf{Cloud \& DevOps:} GCP, Azure, AWS, OCI, Kubernetes (CKAD), Docker, Terraform, Git, Jenkins.
        \item \textbf{Databases:} Oracle, PostgreSQL, MongoDB, Cassandra, Neo4j.
    \end{itemize}

% --- CERTIFICATIONS ---


    \section{Certifications (Selected 2020--2025)}
    \begin{multicols}{2}
        \begin{itemize}
            \item \textbf{GCP:} Prof. Cloud Architect, Network Engineer, ML Engineer, GenAI Leader (2025).
            \item \textbf{Azure:} AZ-900, DP-900, AI-900, SC-900.
            \item \textbf{OCI:} Architect Professional, Developer Associate, AI Foundations (2025).
            \item \textbf{DevOps:} CKAD (Kubernetes), AWS Cloud Practitioner.
            \item \textbf{Data:} Apache Cassandra 3 Dev, Neo4j Prof.
            \item \textbf{Awards:} 20 Codility Golden Awards.
        \end{itemize}
    \end{multicols}

% --- EDUCATION ---


    \section{Education}
    \noindent \textbf{AGH University of Science and Technology, Cracow} \hfill \textbf{2003 -- 2006} \\
    M.Sc. in Computer Science (Computer Systems)

    \noindent \textbf{Cracow University of Economics} \hfill \textbf{2007 -- 2008} \\
    Postgraduate in Economy (Financial Markets Analysis)

% --- LANGUAGES ---


    \section{Languages}
    English (Advanced), Polish (Native), German (Basic).

\end{document}